---
title: "Just a test"
author: "RK"
date: "August 27, 2017"
---

```{r setup, echo=F, output="hide", message=F, warning=F}
library(dplyr)
library(magrittr)
library(knitr)
library(ggplot2)
library(ggthemes)
knitr::opts_chunk$set(cache=TRUE, autodep=TRUE)
```

## R Markdown

This part comes from an `R Markdown` file. This means, that now I can
include arbitrary chunks with `R` code here. For example, there are
`r nrow(mtcars)` rows in the `mtcars` dataset.

This code uses `kable` function to create a nicely-rendered table, like
Table \ref{tbl:cars}.

```{r cars}
kable(mtcars[1:3, ], caption="\\label{tbl:cars}First three rows
      from the `mtcars` dataset.")
```

We can ask `kable` to make fancy floating tables using \LaTeX{}, like Table
\ref{tbl:float_tbl}. They are quite customizable.

```{r latex_table}
iris %>% head(4) %>% kable(format="latex", digits=2, row.names=T,
  caption="\\label{tbl:float_tbl}Floating table")
```

### Python?!

\begin{wrapfigure}[6]{r}{40mm}
  \hfill\includegraphics[width=35mm]
    {imgs/scatterplot.pdf}
\end{wrapfigure}

Since `knitr` and `RStudio` support `Python` as well, we can insert `Python`
chunks into the document! However, we have to care about image saving ourselves.
Another problem is about environments: `R` uses one environment for all chunks
in the document, but each `Python` chunk do not know anything about other
`Python` chunks in the same document.

```{python include=T, eval=F}
import numpy as np
from matplotlib import pyplot as plt

N = 50
x, y, colors = (np.random.rand(n) for n in [N, N, N])
area = np.pi * (15 * np.random.rand(N))**2  # 0 to 15 point radii

f = plt.figure(figsize=(3,2))
plt.scatter(x, y, s=area, c=colors, alpha=0.5)
plt.title("Matplotlib scatterplot")
plt.savefig("imgs/scatterplot.pdf")
```

## Tricks with images

### Size specification

If image is saved into PDF, it will have exactly the same size on
paper as specified in `knitr` (either in the `YAML` header or in the chunk
options). PNG seems to also work fine.

```{r tiny_ggplot_png, echo=FALSE, fig.width=1, fig.height=0.8, fig.cap="Tiny `ggplot2` figure, $1\\times0.8$ inches, PNG\\label{fig:tiny_ggplot_png}", dev="png", dpi=300}
ggplot(mtcars, aes(wt, mpg, col=factor(cyl))) +
    geom_point(alpha=0.75) +
    scale_colour_discrete(guide=F) +
    theme(text=element_text(size=7))
```

### Pack several `ggplot2` or `lattice` images together

For `ggplot2`, use function `ggplotGrob()` from `gridExtra`, then pack images as you need using `cbind()` and `rbind()` – see example in Fig \ref{fig:six_plots}. If you need to combine `ggplot2` with `lattice`, use other funcs from `gridExtra`.

```{r ggplot_many_plots, fig.cap="\\label{fig:six_plots}Alignment of plots using `ggplot2`, `rbind`/`cbind` and `ggplotGrob`."}
suppressMessages(library(gridExtra, warn.conflicts = F))
p <- ggplot(mtcars, aes(x=mpg, col=factor(cyl))) +
    scale_color_brewer("Set1", guide=F)
a <- p + geom_point(aes(y=hp))
b <- p + geom_point(aes(y=qsec))
t1 <- theme_classic()
t2 <- theme_wsj()
t3 <- theme_igray()

f <- ggplotGrob

rbind(cbind( f(a+t1), f(a+t2), f(a+t3) ),
      cbind( f(b+t1), f(b+t2), f(b+t3) )) %>% plot
```

### Mathematical formulae in (`r`)`markdown`

You can insert formulas into a `markdown` files using dollar signs like this
`$E=mc^2$` which gives $E=mc^2$. But make sure that you have *no* whitespaces
between the formula and the surrounding `$`, and no digits follow
immediately after the closing `$`. More details can be found in the
pandoc manual, section *tex_math_dollars*.

\input{../content/04_pure_latex}

