---
title: "Just a test"
author: "RK"
date: "August 27, 2017"
output:
  html_document:
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: tango
    theme: flatly
  md_document:
    dev: pdf
bibliography: refs.bib
---

```{r setup, echo=F, output="hide", message=F, warning=F}
library(dplyr)
library(magrittr)
library(knitr)
library(ggplot2)
library(ggthemes)
```

## R Markdown

This part comes from an `R Markdown` document. This means, that now I can
include arbitrary chunks with `R` code here. For example, there are
`r nrow(mtcars)` rows in the `mtcars` dataset.

This code uses `kable` function to create a nicely-rendered table, like
Table \ref{tbl:cars}.

```{r cars}
kable(mtcars[1:3, ], caption="\\label{tbl:cars}First three rows
      from the `mtcars` dataset.")
```

We can ask `kable` to make fancy floating tables using \LaTeX{}, like Table
\ref{tbl:float_tbl}. They are quite customizable.

```{r latex_table}
iris %>% head(4) %>% kable(format="latex", digits=2, row.names=T,
  caption="\\label{tbl:float_tbl}Floating table")
```

### Python?!

Since `knitr` and `RStudio` support `Python` as well, we can insert `Python`
chunks into the document! However, we have to care about image saving ourselves.
Another problem is about environments: `R` uses one environment for all chunks
in the document, but each `Python` chunk do not know anything about other
`Python` chunks in the same document.

```{python include=F, eval=T, dev="png"}
import numpy as np
import matplotlib.pyplot as plt

N = 50
x, y, colors = (np.random.rand(n) for n in [N, N, N])
area = np.pi * (15 * np.random.rand(N))**2  # 0 to 15 point radii

f = plt.figure(figsize=(3,2))
plt.scatter(x, y, s=area, c=colors, alpha=0.5)
plt.title("Matplotlib scatterplot")
plt.savefig("scatterplot.pdf")
```

![This figure was dynamically generated in Python](scatterplot.pdf){ width=30% }


## Tricks with images

### Size specification

If image is saved into PDF format, then it will have exactly the same size on
paper as specified in `knitr` (either in the `YAML` header or in the chunk
options). However, often PNG works fine as well.

```{r tiny_ggplot_png, echo=FALSE, fig.width=3, fig.height=2, fig.cap="Tiny `ggplot2` plot, $3\\times2$ inches, PNG\\label{fig:tiny_ggplot_png}", dev="png", dpi=300}
ggplot(diamonds, aes(x=price, fill=cut)) +
    geom_density(alpha=0.25) +
    theme(text=element_text(size=7)) +
    facet_wrap("clarity")
```

### Pack several images together

For `ggplot2`, use function `ggplotGrob()` from `gridExtra`. If you need to combine `ggplot2` with `lattice`, use other funcs from `gridExtra`.

```{r ggplot_many_plots, fig.cap="Alignment of plots using `ggplot2`, `rbind`/`cbind` and `ggplotGrob`."}
suppressMessages(library(gridExtra, warn.conflicts = F))
p <- ggplot(mtcars, aes(x=mpg, col=factor(cyl))) +
    scale_color_brewer("Set1", guide=F)
a <- p + geom_point(aes(y=hp))
b <- p + geom_point(aes(y=qsec))
t1 <- theme_classic()
t2 <- theme_wsj()
t3 <- theme_igray()

f <- ggplotGrob

rbind(cbind( f(a+t1), f(a+t2), f(a+t3) ),
      cbind( f(b+t1), f(b+t2), f(b+t3) )) %>% plot
```



\input{../content/04_pure_latex}

